%
% Modified by Sameer Vijay
% Last Change: Wed Jul 27 2005 13:00 CEST
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Sample Notre Dame Thesis/Dissertation
% Using Donald Peterson's ndthesis classfile
%
% Written by Jeff Squyres and Don Peterson
%
% Provided by the Information Technology Committee of
%   the Graduate Student Union
%   http://www.gsu.nd.edu/
%
% Nothing in this document is serious except the format.  :-)
%
% If you have any suggestions, comments, questions, please send e-mail
% to: ndthesis@gsu.nd.edu
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Appendix
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{GNU GENERALISMS}

\section{Definitions}

Several definitions are presented in Table~\ref{tbl:defs} to show both
how to do rotated, line-spanning tables, as well as to define some
commonly used Gnu terms.

\begin{landscape}
\begin{table}
\centering
\caption{Commonly used \NoCaseChange{Gnu} Terms \label{tbl:defs}}
\begin{tabular}{lp{5in}}
\toprule
Term & \multicolumn{1}{c}{Definition} \\
\midrule
Gnu & Small furry animal that is related to the squirrel 
(although they won't admit it). \\
LoG & Abbreviation for the ``Leader of Gnus''.  See
Chapter~\ref{chap:golfing}. \\
Twizzlers & Red, twisty candy that is among the most favorite of Gnu
foods.  Gnus frequently appear overly cute and friendly to humans
bearing twizzler packages.  This is known as ``trolling for twizzlers''
among the Gnus. \\
\bottomrule
\end{tabular}
\end{table}
\end{landscape}

Finally, Table~\ref{tbl:rotated-rankings} shows the top ten Gnus from
Table~\ref{tbl:votes} ranked in order by their aggregate score (along
with some of the raters' comments).  This follows a long-standing Gnu
tradition of self-improvement through public announcement of score
(which some associate with military
origins~\citep{galmira98:_gnus_milit}).  Indeed, this very table has
been observed in the Gnu lodge where it was posted for peer review
\citep{gairley2000}.


\begin{landscape}
% set the caption width to be somewhat short since our table is narrow
% Notice the special commands that we use here to get the right line in the
% table.  Using \hrule is *not* the Right Thing to do here -- use
% \cmidrule.  We use the LaTeX \newcommand simply for convenience.
%
% The longtable package does some nasty voodoo to make \hline work OK.
% So on with the goods
\setlength\LTcapwidth{4.5in}
\begin{longtable}{lcp{4.5in}}
% Note that after the caption line we remove 2em worth of space but in the
% longtable of Chapter 2 we only remove 1em.  This is because a normal 
% \toprule has no space above it, but here we are using cmidrule which does 
% have padding above which we must account for.
  \caption{Top Ten \NoCaseChange{Gnus} From
    Table~\NoCaseChange{\ref{tbl:votes}} With Reviewer Comments.
    \NoCaseChange{Gnus} are Listed Below in Alphabetic Order.
    \label{tbl:rotated-rankings} }\\
  \toprule
  Candidate & Aggregate score & \multicolumn{1}{c}{Reviewer Comments}\\
  \midrule
\endfirsthead
  \caption[]{{\em Continued}} \\  % Just like in Chp. 2
  \midrule
  Candidate & Aggregate score & \multicolumn{1}{c}{Reviewer Comments}\\
  \midrule
\endhead
\endfoot
  \bottomrule
\endlastfoot
George & 7.6 & George is an excellent candidate for the LoG.
  Slightly low C, but hopefully, this 7.6 will be high enough! \\
Glen & 7.2 & A little weak on AM and Fr, but good scores overall.  One
  or two more years of experience should be enough. \\
Goldie & 7.0 & Dismal score in Fr; suspect it had something to do with
  strenuous weight loss program this past year. \\
Gillian & 6.9 & Excellent C, but a little shabby on the Fu.  Suggest
  more roughage. \\
Gibby & 6.9 & Reasonable scores, but need to work on Fr.  Gibby is
  definitely not a morning Gnu. \\ 
Genaveve & 6.5 & Very low Fr; perhaps more coffee?  Suggest practicing
  ``cute faces'' in the mirror several hours per day.  \\
Giovani & 6.2 & Very low Fr; suspect hanging out with Genaveve too
  much. \\
Gina & 6.2 & Mediochre Fu, somewhat low AM.  Perhaps a future in
  marketing or advertising? \\
Garrick & 6.2 & Fairly low AM.  Fu could be better as well; buy a
  comb.  And a mirror.  Immediately.  \\
Gardenia & 6.0 & Dismal AM; very low Fu.  Seems to care more about
  meeting agendas than personal appearance. \\
\end{longtable}
\end{landscape}


% % uncomment the following lines,
% if using chapter-wise bibliography
%
% \bibliographystyle{ndnatbib}
% \bibliography{example}
