\documentclass[10pt]{article}

\usepackage{url}

\begin{document}
\begin{center}
    \textbf{Getting Started with the Notre Dame\\ LaTeX Dissertation Style Package}
\end{center}

\begin{flushright}
    2018-08-01
\end{flushright}

There is a LaTeX class file to help you with creating dissertations
conforming to the Notre Dame Graduate School formatting requirements.

\begin{center}\textit{Quick Start}\end{center}

\begin{enumerate}
    \item Download files: \begin{enumerate}
            \item Visit \url{github.com/ndlib/nddiss}
            \item Choose the green button ``Clone or download''
            \item Select ``Download ZIP''
            \item Save and expand the zip file
        \end{enumerate}
    \item Inside the zip file is an example directory. Copy this and use it as a template if you have not already begun your dissertation.
    \item Copy the files \texttt{nddiss2e.bst} and \texttt{nddiss2e.cls} into whatever directory your dissertation is in. (e.g. your copy of the example directory).
    \item If you are using the example directory, compiling it with LaTeX should work at this point.
    \item If you already have a dissertation file, you will need to set up the formatting in it to parallel the structure in the example file.
    \item There is a manual to explain everything in more detail. See the file \texttt{nddiss2e.pdf}. It is also available online at 
\url{github.com/ndlib/nddiss/blob/master/nddiss2e.pdf}
\end{enumerate}

Email Don Brower (\url{dbrower@nd.edu}) for assistance and questions.

\begin{center}\textit{Resources}\end{center}
\begin{itemize}
    \item If you have never used LaTeX before, the Navari Family Center for Digital Scholarship offers workshops to learn LaTeX.
        \url{cds.library.nd.edu}
    \item The current Graduate School formatting requirements:
        \url{graduateschool.nd.edu/resources-for-current-students/dt/dt-resources}
    \item A useful general reference for LaTeX is the LaTeX Wikibook:
        \url{en.wikibooks.org/wiki/LaTeX}
\end{itemize}

\end{document}
